Analysing a carcinoma dataset with the hyper2 package

### 2025-04-27 inst/carcinoma.Rmd
typo

<font size="1"> (takes about fifteen minutes to run without cache; the
value of `carcinoma_maxp` is calculated separately [discussed below],
and that takes a few days to run.  </font>

>>>>

<font size="1"> (takes about fifteen minutes to run without cache; the
value of `carcinoma_maxp` is calculated separately [discussed below],
and that takes a few days to run).  </font>
